**Density Dependence**

### 2023-02-09 Rmd/ddMac.Rmd
hopefully now works

  om2=ddFn(year,om2,par)
  om2=fwd(om2,f=f[,year],sr=eq)
  }

catch(om2)=computeCatch(om2,slot="all")
plot(window(FLStocks("OM"=om,DD=om2),start=400))
```

@@

```{r, check2} 
ggplot(model.frame(FLQuants(om2[,dim(m(om2))[2]],"Biomass"=biomass,"Yield"=catch)))+  
  geom_line(aes(Biomass,Yield),col="black")+ 
  geom_line(aes(Biomass,Yield),data=model.frame(FLQuants(om[,dim(m(om))[2]],"Biomass"=biomass,"Yield"=catch)),col="red")
```

>>>>

  om2=ddFn(year,om2,par)
  om2=fwd(om2,f=f[,year],sr=eq)
  }
catch(om2)=computeCatch(om2,slot="all")
```

```{r, check2}
plot(window(FLStocks("OM"=om,DD=om2),start=40))
```

@@

```{r, check3} 
ggplot(model.frame(FLQuants(om2[,dim(m(om2))[2]],"Biomass"=biomass,"Yield"=catch)))+  
  geom_line(aes(Biomass,Yield),col="black")+ 
  geom_line(aes(Biomass,Yield),data=model.frame(FLQuants(om[,dim(m(om))[2]],"Biomass"=biomass,"Yield"=catch)),col="red")
```
